Deep Reinforcement Learning for Conservation Decisions

### 2021-06-10 manuscript/presubmission-letter.Rmd
Edits presubmission letter

To date, the uncertain and changing environments considered by RL research have largely been drawn from examples in robotic movement and video games. *Nature* recently featured RL agents achieving superhuman performance on classic Atari games, and *Science* described the success of Deepmind's AlphaZero against grandmasters in Go, Chess, and Shogi. We believe that similar techniques could improve decision-making in managing ecological environments as well. <!-- Having trouble reconciling lines 21-23, trying to say that these simulators are like the grand challenges and given RL's track record of solving intractable decision-making problems, perhaps RL could shed light here? I think having a sentence asserting that RL would use ecological models not replace them would be good somewhere in here.--> Already, complex ecological simulators -- SORTIE in forest ecosystems, EcoPath with EcoSim in marine systems, GCM models in climate -- are the Atari games of our policy grandmasters. <!-- Kari: possible rewrite of the following sentence, not sure if it helps --> While existing process-based models allow a window into the future scenarios of ecological management, RL has the potential to find optimal solutions in those spaces. Drawing on examples from fisheries management, ecosystem tipping points, and wildfire spread, we illustrate how ecological models and simulations can be used to successfully train RL agents that match or exceed the performance of available management strategies. Although our examples are primarily a proof-of-principle, they serve to illuminate both the promise as well as potential pitfalls.

>>>>

To date, the uncertain and changing environments considered by RL research have largely been drawn from examples in robotic movement and games. *Nature* recently featured RL agents achieving superhuman performance on classic Atari games, *Science* described the success of Deepmind's AlphaZero against grandmasters in Go, Chess, and Shogi. We believe that similar techniques could improve decision-making in managing ecological environments as well. Already, complex ecological simulators -- SORTIE in forest ecosystems, EcoPath with EcoSim in marine systems, GCM models in climate -- are the Atari games of our policy grandmasters. Detailed, process-based models allow a window into the future scenarios of ecological management. Drawing on examples from fisheries management, ecosystem tipping points, and wildfire spread, we illustrate how ecological models and simulations can be used to successfully train RL agents that match or exceed the performance of available management strategies. Although our examples are primarily a proof-of-principle, they serve to illuminate both the promise as well as potential pitfalls.
